Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-22 paper/paper.tex
#28 clarification

By contrast, almost all the coefficients in Columns (2), (3) and (4) are insignificant, suggesting that no particular subset of construction is driving the results.

>>>>

By contrast, almost all the coefficients in Columns (2), (3) and (4) are insignificant, suggesting that neither of these specific subsets of construction is driving the results.
